Reliable Inferences from Simply Parameterised Models

### 2012-08-29 ms.tex
Chi squared
Emission line figure
Editing of intro

\begin{itemize}
\item Define terminology very carefully, present Bayes' rule \\
\item Describe the ``joint'' (parameters $\times$ data space) view of inference, describe how the form of the likelihood function is prior information \citep{caticha} \\
\item Discuss use of MCMC techniques for complex problems \\
\item Discuss the various attempts at robustness/model checking/elicitation and that stuff
\end{itemize}

Bayesian Inference is a powerful framework for modelling uncertainty that has
been successfully applied in many scientific fields \citep{}. The basic idea
is that we can model the degree of plausibility of a hypothesis $H$ by a real
number in $[0, 1]$, and that these numbers should be manipulated according to
the rules of probability theory. If we are initially uncertain about some
hypothesis $H$, we model this as a {\it prior probability} $P(H)$. If some other
hypothesis $D$ is discovered to be true, the plausibility of $H$ is updated to
the {\it posterior probability} using Bayes' rule:
\begin{equation}
P(H|D) = \frac{P(H)P(D|H)}{P(D)}
\end{equation}

One common application of Bayesian Inference is for parameter estimation.
Suppose there is some quantity $\theta$ that is unknown. Initially, we describe
our uncertainty by a prior distribution $p(\theta)$. We also know about some
observation or experiment that will yield data $D$ that will provide some
information about $\theta$. We describe our knowledge about this process by 
{\it sampling distributions} $p(D|\theta)$. Then, once a specific data set
$D_{\rm obs}$ has been observed, we update our state of knowledge about $\theta$
to the {\it posterior distribution}:
\begin{equation}
p(\theta | D) \propto p(\theta) p(D|\theta)|_{D=D_{\rm obs}}
\end{equation}
The various terms in this equation have the following names and meanings.

@@

\item $p(\theta)$ is the {\it prior distribution}, a probability distribution
over possible values for $\theta$ that describes our uncertainty about
$\theta$ before taking into account the data. Commonly, this is a broad
probability distribution, describing a large amount of uncertainty. \\

\item $p(D|\theta)$ is a function of
both $\theta$ and $D$ and is referred to as the {\it sampling distribution}. 
The sampling distribution $p(D|\theta)$ is a set of probability distributions,
one for each value of $\theta$, and describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}.

@@

@@

\begin{eqnarray}
p(\yy|A, c, w) &=& \prod_{i=1}^N
\frac{1}{\sigma\sqrt{2\pi}}
\exp
\left[
-\frac{1}{2\sigma^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
\right].
\end{eqnarray}

>>>>

Bayesian Inference is a powerful framework for modelling uncertainty that has
been successfully applied in many scientific fields. The basic idea
is that we can model the degree of plausibility of a hypothesis $H$ by a real
number in $[0, 1]$, and that these numbers should be manipulated according to
the rules of probability theory. If we are initially uncertain about some
hypothesis $H$, we model this as a {\it prior probability} $P(H)$. If some other
hypothesis $D$ is discovered to be true, the plausibility of $H$ is updated to
the {\it posterior probability} using Bayes' rule:
\begin{equation}
P(H|D) = \frac{P(H)P(D|H)}{P(D)}
\end{equation}

One common application of Bayesian Inference is for parameter estimation.
Suppose there is some quantity $\theta$ that is unknown. Initially, we describe
our uncertainty by a prior probability distribution $p(\theta)$. We also know about some
observation or experiment that will yield data $D$ that will provide some
information about $\theta$. We describe our knowledge about this process by a 
set of conditional probability distributions $p(D|\theta)$. Then, once a specific data set
$D_{\rm obs}$ has been observed, we update our state of knowledge about $\theta$
to the {\it posterior distribution}:
\begin{equation}
p(\theta | D) \propto p(\theta) p(D|\theta)|_{D=D_{\rm obs}}
\end{equation}
The various terms in this equation have the following names and meanings.

@@

\item $p(\theta)$ is the {\it prior distribution}, a probability distribution
over possible values for $\theta$ that describes our uncertainty about
$\theta$ before taking into account the data. In many applications, this is a broad
probability distribution describing a large amount of uncertainty. \\

\item $p(D|\theta)$ is a function of
both $\theta$ and $D$ and is sometimes referred to as the {\it sampling distribution}.
Another name is the generative model. 
The sampling distribution $p(D|\theta)$ is a set of probability distributions,
one for each value of $\theta$, and describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}. In particular, it is the probability distribution
for the data we might observe, {\it if} we knew the true value of the parameters
$\theta$, as a function of $\theta$.

@@

{\bf Discuss the various attempts at robustness/model checking/elicitation and that stuff}

@@

\begin{eqnarray}
p(\yy|A, c, w) &=& \prod_{i=1}^N
\frac{1}{\sigma\sqrt{2\pi}}
\exp
\left[
-\frac{1}{2\sigma^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
\right] \\
&\propto& \exp\left[-\frac{1}{2\sigma^2}\sum_{i=1}^N\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2\right] \\
&\propto& \exp\left[-\frac{1}{2}\chi^2\right].
\end{eqnarray}

\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{emission_line.eps}
\end{center}
\end{figure*}
